\documentclass{simplecv}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Content here 
\begin{document}

% Heading 

\begin{center}
    \textbf{\Huge \scshape Rahul Seth} \\ \vspace{3pt}
    \small
    \faMobile\hspace{.5pt} \href{tel:919717861405}{+91 9717 861 405}
    $|$
    \faAt\hspace{.5pt} \href{mailto:srahulseth7@gmail.com}{srahulseth7@gmail.com}
    $|$
    \faLinkedinSquare\hspace{.5pt} \href{https://www.linkedin.com/in/rahuls7}{LinkedIn}
    $|$
    \faGithub\hspace{.5pt} \href{https://github.com/sethr07}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{}{Dublin, Ireland}
\end{center}

% Education

\section{Education}
    \vspace{3pt}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Trinity College, Dublin}{Ireland}
    {BAI Computers and Electronics Engineering}{2018 \textbf{--}2022}

    \resumeProjectHeading{\textbf{Dissertation: ``Surveying Long-Term Cryptographic Keys in Ireland"} $|$ \emph{\href{https://github.com/sethr07/Final-Year-Project}{\color{blue}GitHub}}}{}
    \resumeItemListStart
        \resumeItem{Developed a network scanner to identify and survey mail servers in Ireland; mining their cryptographic data}
        \resumeItem{Extracted TLS/SSH session metadata using custom-made JSON schema and processed it using Python}
        \resumeItem{Modelled public key sharing for ~20000 hosts across all standard ports by clustering on SHA-256 fingerprint}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
    
% Work Ex
\section{Work Experience}
    \vspace{3pt}
    \resumeSubHeadingListStart

    \resumeSubHeadingWithPromoitions
    {Baker Hughes}
    {Ireland}
    {Graduate Software Engineer}
    {Aug'22 - March'23}
    {
        \resumeItem{Developed an HMI emulator for testing and client training, saving development time and reducing hardware needs.}
        \resumeItem{Authored Python scripting for automation of tasks like bitmap to C conversion and batch builds, saving 3 hours per feature.}
        \resumeItem{Optimised Agile boards by decomposing user stories into tasks and coordinating sprints; increased productivity by 8\%.}
    }
    {Software Engineer}
    {Mar'23 - Present}
    {
        \resumeItem{Played key role in product development; aimed at modernizing a legacy oxgyen sesnor with enhanced UI/UX.}
        \resumeItem{Spearheaded the design and development of the product's LCD interface, implementing sophisticated navigation algorithms and establishing robust code architecture.}
        \resumeItem{Led initiation of CI/CD GitHub pipeline using Parasoft; automated code analysis and reduced rework by 29\%.}
        \resumeItem{Handled bootloader integration and linked Data Manager with HMI, bolstering system functionality and user interaction.}
        \resumeItem{Established standardized product design practices with other Engineers, developing a globally accessible Python-based icon library to unify visual elements across all products.}
    }

    \vspace{3pt}

    \resumeSubheading{Ericsson}{India}
    {ML Intern}{{June'21 \textbf{--} Aug'21}}
    \resumeItemListStart
        \resumeItem{Analysed large datasets; applied ML models like Linear Regression, Decision Trees, and AdaBoost for predictive analysis.}
        \resumeItem{Utilised 5 performance metrics including recall, f1score, precision, accuracy and ROC curves to assess the performance.}
        \resumeItem{Applied K-Means algorithm on the historical IT dataset; hyper-tuned the model using elbow curves, and silhouette method to identify optimal clusters.}
    \resumeItemListEnd

    \resumeSubheading{Lepton Software}{India}
    {Market Research Intern}{{June'19 \textbf{--} Aug'19}}
    \resumeItemListStart
        \resumeItem{Leveraged advanced Excel functions like vlookups, pivot tables, and sorts to perform in-depth analysis of 5G market data.}
        \resumeItem{Presented to stakeholders a strategy on how Lepton can differentiate itself from competitors by leveraging services they offer.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

% Projects 
\section{Projects and Activities}
    \vspace{3pt}
    \resumeSubHeadingListStart

    \resumeSubheading{BCG Gamma}{Virtual}
    {Data Science}{{June'21 \textbf{--} Aug'21}}
    \resumeItemListStart
        \resumeItem{Enhanced understanding of problem-solving processes and working with challenging data analysis tasks.}
        \resumeItem{Developed practical experience in business problem framing, exploratory data analysis, feature engineering, predictive modeling, and turning insights into business decisions.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{Email Client}}{}
    \resumeItemListStart
        \resumeItem{Designed an email client for macOS (Unix) architectures; incorporated features like login, search, compose and schedule send}
        \resumeItem{Implemented the backend and API calls using Python and utilised Kivy for UI design}
        \resumeItem{Utilised Docker container to package the application for simplified distribution and accessibility in opensource }
    \resumeItemListEnd

    \resumeSubheading{Formula Trinity}{Ireland}
    {State Estimation and Path Planning}{{Nov'20 \textbf{--} May'22}}
    \resumeItemListStart
        \resumeItem{Implemented Kalman and Particle Filters to minimise data noise and localise racing map for usage by other teams.}
        \resumeItem{Led state estimation team of 5; utilised data from 3 sensors on the autonomous car to determine the car’s position on tracks.}
    \resumeItemListEnd

    \resumeSubheading{Trinity Indian Society}{Ireland}
    {Vice Presedient}{Sep'18 \textbf{--} June'19}
    \resumeItemListStart
        \resumeItem{Led a team of 10 dealing with logistics for organising Indian cultural events like Holi and Diwali}
        \resumeItem{Participated in funding pitches and won a 350 Euro grant from BOI used for marketing campaigns.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

% Skills
\section{Skills}
\vspace{3pt}
\resumeSubHeadingListStart
\small{\item{
    \textbf{Programming: }{C, C++, Python, SQL, XML, Git, Matlab, Verilog, JavaScript, R, Static Analysis, OOP} \\ \vspace{3pt}

    \textbf{Technologies: }{GitHub, IAR, Parasoft, PostreSQL, Visual Studio, Linux, Wireshark, SPSS}
}}
\resumeSubHeadingListEnd

\end{document}