\documentclass{../templates/coverletter}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}
\usepackage{mathptmx} % for Times font
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\usepackage{xcolor}
\definecolor{timberwolf}{rgb}{0.86, 0.84, 0.82}

\companyname{Oliver Wyman, Marsh McLennan}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\usepackage[pages=some]{background}
\backgroundsetup{
  scale=1,       %% change accordingly
  color=black,   %% change accordingly
  opacity=1,     %% change accordingly
  angle=0,       %% change accordingly
  contents={%
  \begin{tikzpicture}[remember picture,overlay]
  \path [fill] (current page.south west) rectangle (current page.north east);
  \end{tikzpicture}}
}


% Content here 
\begin{document}
\BgThispage

\onehalfspacing

\name{Rahul Seth}

\greeting
\subject{Data Scientist -- Data and Analytics (DNA)}

\makeatletter
\opening
{
    I am writing to apply for the Associate Data Scientist role at your company. I have decided to relocate back to India from Ireland. 
    I am a software engineer from Trinity College with a strong foundation in C, C++, Python, and JavaScript. 
    My work has spanned projects using Keras, Sklearn, TensorFlow, and Pandas, focusing on deep learning concepts. 
    I also bring hands-on machine learning experience from my internship at Ericsson's AI/ML team. Currently, in
    my current job at Baker Hughes, .
}
\makeatother

\workex 
{
    At Baker Hughes, I leverage C and Python to craft software for embedded devices and collaborate on 
    product initiatives that involve design revamps and feature integration. As part of an eight-person team,
    I regularly engage with senior engineers, learning to collaborate effectively and implement 
    agile methodologies. This approach has sharpened my time management skills and prioritized punctual 
    project delivery. My responsibilities also include designing and developing the complete Human-Machine
    Interface (HMI) for the device, involving routine code reviews and technical presentations. Furthermore, 
    I have worked with diverse teams to standardize design practices, enhancing decision-making efficiency
    and clarity across the organization.enhance clarity across projects.
}

\workex
{
    In addition to my hands-on experience with data at Ericsson and during my dissertation research, I am 
    eager to leverage my programming skills to deliver analytical solutions as an Associate Data Scientist at 
    your company. My previous roles have allowed me to cultivate a strong understanding of working within 
    cross-functional teams, a skill set I am keen to further develop. I am particularly attracted to the
    challenge of developing highly scalable solutions, as I understand it demands an additional layer of
    strategic thinking and problem-solving. 
}

\makeatletter
\conclusion
{
    My goal in applying for this role is to significantly contribute to the field of Data Science. A strong
    fascination for data and numbers motivates me to continually expand my knowledge and expertise. I
    resonate deeply with the ethos of the book \textit{Automating the Boring Stuff}, which emphasizes the use
    of technology to streamline processes – a philosophy I strive to apply in my daily work. I am particularly
    interested in joining Marsh McLennan due to its well-known culture of continuous learning and collaboration.
    Having connected with colleagues who have worked within the organization in Ireland, I am confident that
    it offers the stimulating environment and exceptional team dynamics that align with my professional
    aspirations.
}
\makeatother

\closing

\signature{Rahul Seth}

\end{document}